### 2024-07-17 SupplementaryMaterials/AppendixScripts/Appendix_initial_QMP_analyses.rmd
Implemented writing feedback, fixed betareg to apa full CI code, and moved the appendix files to the supplementary materials.

# Initial Coding Protocol QMP Analyses

@@

For hypothesis 5, a logistic regression model was used to test the association between the QMP ratio in replication protocols and replication success. In this appendix we run the model based on the QMP ratios obtained using the initial protocol.

@@

H5_test_results_with_OR <- OR_to_apa_full_supplier(H5_test_results$full_result$QMP_ratio, negative_b = TRUE)

@@

The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model.

@@

Appendix B already contained the results of the multilevel sensitivity models for hypothesis 5 & 6 based on the QMP ratios obtained using the revised coding protocol. In this appendix we show the result for the same models based on the QMP ratios obtained using the initial protocol.

@@

### Results + Comparison Interpretation
The figure below displays the distribution of observed QMP ratios across original articles and replication protocols based on the initial coding protocol.

@@

Similarly to the previous test, the relation was not significant for the QMP ratios obtained with the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`). Thus, not supporting hypothesis 6. Figure \@ref(fig:Plot46InitialDataCode) displays this relationship visually.

@@

Table \@ref(tab:H6ExploratoryAssociationsInitialTable) shows the relations between original and replication QMP ratios for each QMP type based on the initial protocol. Figure \@ref(fig:Plot46FullInitialDataCode) shows the same relations displayed visually.

@@

Now looking at the multilevel sensitivity analyses (see appendix B), only now using the QMP ratios based on the initial coding protocol.

Contrary to the results of the multilevel sensitivity model testing hypothesis 5 using QMP ratios obtained with the revised coding protocol, the relationship in the multilevel model was no longer significant for QMP ratios obtained with the initial coding protocol (`r check_h5$full_result$hypothesis_supportTRUE`).

>>>>

```{r analysis-preferences}
# Seed for random number generation
set.seed(17042023)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Appendix D: Initial Coding Protocol QMP Analyses

@@

For hypothesis 5, a logistic regression model was used to test the association between the QMP ratio in replication protocols and replication success. In this appendix we run the model based on the QMP ratios obtained using the initial protocol. The relation between QMP ratios in the replication protocols and corresponding original articles were investigated using a beta regression model. Appendix B already contained the results of the multilevel sensitivity models for hypothesis 5 & 6 based on the QMP ratios obtained using the revised coding protocol. In this appendix we show the result for the same models based on the QMP ratios obtained using the initial protocol.

@@

H5_test_results_with_OR <- OR_to_apa_full_supplier(H5_test_results$full_result$QMP_ratio, negative_b = TRUE, not_significant = TRUE)

@@

@@

@@

### Results & Comparison Interpretation
The figure below displays the distribution of observed QMP ratios across original articles and replication protocols based on the initial coding protocol.

@@

Similarly to the previous test, the relation was not significant for the QMP ratios obtained with the initial protocol (`r betareg_output_to_apa_full(H6_test_results)`). Thus, not supporting hypothesis 6. Figure \@ref(fig:Plot46InitialDataCode) displays this relationship visually. Table \@ref(tab:H6ExploratoryAssociationsInitialTable) shows the relations between original and replication QMP ratios for each QMP type based on the initial protocol. Figure \@ref(fig:Plot46FullInitialDataCode) shows the same relations displayed visually.

@@

@@

Now looking at the multilevel sensitivity analyses (see appendix B), only now using the QMP ratios based on the initial coding protocol. Contrary to the results of the multilevel sensitivity model testing hypothesis 5 using QMP ratios obtained with the revised coding protocol, the relationship in the multilevel model was no longer significant for QMP ratios obtained with the initial coding protocol (`r check_h5$full_result$hypothesis_supportTRUE`).

### 2024-07-17 SupplementaryMaterials/AppendixScripts/Appendix_multilevel_analyses.rmd
Implemented writing feedback, fixed betareg to apa full CI code, and moved the appendix files to the supplementary materials.

# Multilevel Analyses

This appendix contains the multilevel model versions of the models used to test Hypothesis 3, 5, & 6. These models were excluded from the published article for the sake of brevity, and because the sample size was not large enough to support multilevel modelling in most cases.

## Hypothesis 3, nested within replication set
### Explanation of Relevance
In this data, replication attempts at different lab locations can be seen as nested within a replication set. To see if this nesting might impact the analyses of hypothesis 3, multilevel models are included here as sensitivity checks.

>>>>

```{r analysis-preferences}
# Seed for random number generation
set.seed(17042023)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Appendix B: Multilevel Analyses

This appendix contains the multilevel model versions of the models used to test Hypothesis 3, 5, & 6. These models were excluded from the main text for the sake of brevity, and because the sample size was not large enough to support multilevel modelling in most cases.

## Hypothesis 3, Nested Within Replication Sets
### Explanation of Relevance
In this data, replication attempts at different lab locations can be seen as nested within a replication set. To see if this nesting might impact the analyses of hypothesis 3, multilevel models are included here as sensitivity checks.

### 2024-07-17 SupplementaryMaterials/AppendixScripts/Appendix_omega_analyses.rmd
Implemented writing feedback, fixed betareg to apa full CI code, and moved the appendix files to the supplementary materials.

# Omega Coefficient Analyses

@@

### explanation why
Omega was included since it has been argued to be a more informative measure of reliability than alpha, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing]. Omega was calculated using the omega function in the *psych* R package [@R-psych]. Default arguments were used in the function except the nfactors argument, which was set to 1.

### Models
To separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable, which was the same model used for testing. The difference was that the omega value of a replication was used as dependent variable in this instance, using the *lmer* function from the *lme4* package [@R-lme4].

@@

The ICC was calculated similarly based on the omega as was done for Cronbach's alpha in the article.

@@

The analysis for H3 related the calculated average reliability coefficients for each replication set to whether the replication was successful when judged at meta-significance level of $alpha <.05$.

@@

A multilevel random-intercept, and a random-slope equivalent model to the model above were also run for Omega, similarly to what was done for Cronbach's alpha in Appendix B.

@@

### Results + Comparison Interpretation
For omega the mean (values calculated in the population across replication sets) was `r apa_num(mean(data_h3_multiple$omega, na.rm = TRUE), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`.

>>>>

```{r analysis-preferences}
# Seed for random number generation
set.seed(17042023)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Appendix C: Omega Coefficient Analyses

@@

### Explanation of Relevance
Omega was included since it has been argued to be a more informative measure of reliability than alpha, while also providing validity evidence for the scale [@crutzen2017scale; @deng2017testing]. We focused our attention on the Cronbach’s Alpha in the main text, because Cronbach’s Alpha is used more commonly in research allowing us to make comparisons between calculated and reported reliabilities. Furthermore, we were able to calculate the standard error of alpha to be used in the Reliability Generalization meta-analysis. Omega was calculated using the omega function in the *psych* R package [@R-psych]. Default arguments were used in the function except the nfactors argument, which was set to 1.

### Models
To separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable, which was the same model used for testing. The difference was that the omega value of a replication was used as dependent variable in this instance, using the *lmer* function from the *lme4* package [*v`r getNamespaceVersion("lme4")[[1]]`*; @R-lme4].

@@

The ICC was calculated similarly based on the omega as was done for Cronbach's alpha in the article. The analysis for H3 related the calculated average reliability coefficients for each replication set to whether the replication was successful when judged at meta-significance level of $alpha <.05$. A multilevel random-intercept, and a random-slope equivalent model to the model above were also run for Omega, similarly to what was done for Cronbach's alpha in Appendix B.

@@

@@

@@

### Results & Comparison Interpretation
For omega the mean (values calculated in the population across replication sets) was `r apa_num(mean(data_h3_multiple$omega, na.rm = TRUE), digits = 3)` with a standard deviation of `r apa_num(sd(data_h3_multiple$omega, na.rm = TRUE), digits = 3)`.

### 2024-07-17 SupplementaryMaterials/AppendixScripts/Appendix_pre-reg_analyses.Rmd
Implemented writing feedback, fixed betareg to apa full CI code, and moved the appendix files to the supplementary materials.

# Pre-registration Analyses

@@

## Intraclasscorelation assessment for within measure variation in reliability

### Pre-registration Analysis Justification & Reason for Omission from Article
Reliabilities could be calculated from the replication datasets. On top of that, reliabilities could be calculated for each individual lab per replication set so that the variance of them could be assessed. To separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable and the Cronbach's alpha or omega value of a replication as dependent using the lmer function from the lme4 package [@R-lme4] t.

@@

To present additional validity evidence alongside the analyses of Cronbach's alpha and omega coefficients, the unidimensionality of each measure was investigated. To test this, each multiple item scalar measure had their factor structure investigated on the entire measure data of the replication set.

@@

For the sake of this analysis the simple heuristic was chosen that if the measure was used as a single composite variable in the analyses, then it should be uni-dimensional. This is somewhat similar to what was done by @shaw2020measurement, but for the sake of this article it was deemed to strong an assumption to make that this heuristic would always hold. For instance, IQ score is often used as a single indicator score, however the construct of IQ is not considered unidimensional, and is instead understood to have many sub-dimensions (e.g. verbal comprehension, perceptual reasoning, etc.). As a result, the use of a single score in the analyses cannot be taken as evidence that the construct is considered unidimensional by neither the authors, nor the broader literature on the topic.

Nevertheless, we present here the result of the analyses made under the assumption that the one score, one dimension heuristic holds, for the readers that are comfortable with this heuristic.

@@

A single factor confirmatory factor analysis was implemented using the *fa* function from the *psych* package [@R-psych] in R. The maximum likelihood factoring method was used, with defaults being used for all other function arguments. From this analysis, the RMSEA of the one factor solution was extracted. Additionally, a parallel test was conducted using the *fa.parallel* function also from the psych package. If either the RMSEA score \< .08, or the parallel analysis returned a one factor solution, unidimensionality was coded as true, otherwise it was coded as false.

@@

Follow-up analyses were preregistered for hypothesis 6. Using a similar model to the main hypothesis test with all unique combination of the five different QMP types being tested across original and replication data. The goal of these analyses was to see if there are any type specific carry-over effects in QMPs between original and replication. Due to the large number of tests, the focus was exploratory using visualization rather than inference.

It is partly this large number of tests, as well as the resulting lack of clear interpretability in the results that caused this analysis to be omitted from the main article. However, for completeness and transparency it is reported here.

>>>>

```{r analysis-preferences}
# Seed for random number generation
set.seed(17042023)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Appendix A: Pre-registration Analyses

@@

## Intraclasscorelation Assessment for Within Measure Variation in Reliability

### Pre-registration Analysis Justification & Reason for Omission from Article
Reliabilities could be calculated from the replication datasets. On top of that, reliabilities could be calculated for each individual lab per replication set so that the variance of them could be assessed. To separate between and within variance in reliability, a multilevel random intercept model was specified with replication set as the grouping variable and the Cronbach's alpha or omega value of a replication as dependent using the *lmer* function from the *lme4* package [*v`r getNamespaceVersion("lme4")[[1]]`*; @R-lme4].

@@

To present additional validity evidence alongside the analyses of Cronbach's alpha and omega coefficients, we investigated the unidimensionality of each measure. To test this, each multiple item scalar measure had their factor structure investigated on the entire measure data of the replication set.

@@

For the sake of this analysis the simple heuristic was chosen that if the measure was used as a single composite variable in the analyses, then it should be uni-dimensional. This is somewhat similar to what was done by @shaw2020measurement, but for the sake of this article it was deemed to strong an assumption to make that this heuristic would always hold. For instance, IQ score is often used as a single indicator score, however the construct of IQ is not considered unidimensional, and is instead understood to have many sub-dimensions (e.g. verbal comprehension, perceptual reasoning, etc.). As a result, the use of a single score in the analyses cannot be taken as evidence that the construct is considered unidimensional by neither the authors, nor the broader literature on the topic. Nevertheless, we present here the result of the analyses made under the assumption that the one score, one dimension heuristic holds.

@@

A single factor confirmatory factor analysis was implemented using the *fa* function from the *psych* package [*v`r getNamespaceVersion("psych")[[1]]`*; @R-psych] in R. The maximum likelihood factoring method was used, with defaults being used for all other function arguments. From this analysis, the RMSEA of the one factor solution was extracted. Additionally, a parallel test was conducted using the *fa.parallel* function also from the *psych* package. If either the RMSEA score \< .08, or the parallel analysis returned a one factor solution, unidimensionality was coded as true, otherwise it was coded as false.

@@

Follow-up analyses were preregistered for hypothesis 6. The pre-registered plan was to make use of contingency tables to compare relations between all five QMP types across original and replication studies. The goal of these analyses was to see if there are any type specific carry-over effects in QMPs between original and replication. Due to the large number of tests, the focus was exploratory using visualization rather than inference.

It is partly this large number of tests, as well as the resulting lack of clear interpretability in the results that caused this analysis to be omitted from the main article. . However, This analysis was anyhow intended not as supplementary to the main test for hypothesis 6. Furthermore, the analyses would regardless have to be changed from the pre-registered analyses to beta-regressions for each unique combination of the QMP categories across original and replication. For completeness and transparency the analyses using beta-regressions are reported here.
